---
title: "Assignments and Gradings Live Session Assignment Unit 2"
author: "Marvin Scott"
date: "May 20, 2016"
output: html_document
---



##R Markdown Document
#Question 1
# a.The log of a positive number
```{r}
log10(1000)
```
# b.The square-root of a positive number
```{r}
sqrt(25)

```
#Question 2
# a.Create a vector of 15 standard normal random variables. 

```{r}
vector1<-runif(15, min=5, max = 27)
vector1
```
# b.Calculate its mean and Standard Deviation.
```{r}
mean(vector1)
sd(vector1)
```
# c.Change the mean to 10 and the SD to 2 and recalculate the vector of 15 random normal variables
```{r}
vector2<-rnorm(15, mean = 10, sd= 2)
vector2

```
#Question 2
# a.The weights of 6 individuals in kg are 60, 72, 57, 90, 95, 72
#   Their heights (in m) are 1.80, 1.85, 1.72, 1.90, 1.74, 1.91
#   Enter these vectors into R
```{r}
wgts_kg<- c(60,72,57,90,95,72)
wgts_kg
hgts_m<-c(1.80, 1.85, 1.72, 1.90, 1.74, 1.91)
hgts_m
```
# b.Create a scatterplot of weight vs. height. Interpret the scatterplot
```{r}
plot(hgts_m,wgts_kg)

```
# c.Calculate the BMI for each individual (BMI = weight in kg divided by the square of the height in m)
```{r}
BMI<- wgts_kg/(hgts_m^2)
BMI
```
# d.Calculate the mean for weight
```{r}
mean(wgts_kg)
```
# e.Subtract the mean from each value of weight
```{r}
l <-mean(wgts_kg)
Subtract_mean<- l - wgts_kg
Subtract_mean
```
# f.Sum the result
```{r}
 sum(Subtract_mean)

```